---
title: "Resume<br><br>"
menu: main
output: 
  html_document:
    df_print: paged
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: false
    theme: united
    highlight: espresso
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
library(knitr)
library(here)
library(lubridate)
library(kableExtra)
library(DT)
library(glue)
library(readxl)
library(stringi)

# install.packages("remotes")
# remotes::install_github("mitchelloharawild/icons")
# install.packages("fontawesome")
library(fontawesome)


#### publications #####
publications <- read_csv("_content/publications.csv")

#### all other entries #####
cv_entries <- read_csv("_content/cv_entries.csv") %>%
  mutate(year_begin = year(date)) %>%
  mutate(year_end = case_when(
    date_end == "present" ~ date_end,
    !is.na(date_end) ~ str_sub(date_end, 1, 4),
    is.na(date_end) ~ date_end
  )) %>%
  mutate(year = ifelse((is.na(year_end) | year_begin == year_end),
                      year_begin,
                      str_c(year_begin, " --- ", year_end)))


blank_year_when_repeated <- function(cv_entry_tibble){
  cv_entry_tibble %>% 
    mutate(row_number = row_number()) %>% 
    mutate(year_begin = as.character(year_begin),
           year_begin = case_when(
             row_number == 1 ~ year_begin,
             year_begin == lag(year_begin) ~ str_c('<span class="repeated-year">', year_begin, '</span>'),
             year_begin != lag(year_begin) ~ year_begin
           )) %>% 
    mutate(year = if_else(!is.na(lag(year)) & lag(year) == year, 
                          str_c('<span class="repeated-year">', year, '</span>'),
                          year))
}
```



# Summary



I am currently a senior Economics major and Data Analytics minor at SUNY Geneseo. 
Following my graduation in May of this year, I will be searching for positions as a
data analyst, particularly in the growing field of sports analytics. I not only have a tremendous knowledge of all major sports, but I understand the power that sports has to bring together communities unite people around a common cause. While the world we live in seems to 
be in constant turmoil, sports has the ability to make us forget all of that and enjoy 
the simple things in life.

My research utilizes econometrics/machine learning to analyze how certain variables affect a player's draft position. To expand even further, I wish to examine if these variables have any correlation in predicting a player's long term success in the league. I will be using draft, combine and college data from the past 20 years for my study. 


::: {}

::::







<br>


# Education
```{r}
cv_entries %>% 
  filter(type == 'education') %>% 
  mutate(what = str_c( "<span class='cv-entry-title'>", 
                              what, "</span>, ", where,
                              "<br>", 
                       ifelse(is.na(additional_info), "", additional_info) 
                       , "<br>", 
                       ifelse(is.na(additional_info2), "", additional_info2))) %>% 
  select(year, what) %>% 
  kbl(padding = 0, col.names = NULL, escape = FALSE) %>%
  kable_styling( bootstrap_options = c("hover", "condensed"))   %>% 
  column_spec(1, width = "15%")

```


<br>

# Work Experience
```{r}
cv_entries %>% 
  filter(type == 'work', is.na(website)) %>% 
  mutate(additional_info = replace_na(additional_info, "")) %>% 
  mutate(what = str_c("<span class='cv-entry-title'>", what, "</span><br class='work-break'>", where, "<br>", additional_info)) %>% 
  arrange(desc(date)) %>% 
  select(year, what) %>% 
  kbl(padding = 0, col.names = NULL, escape = FALSE) %>%
  kable_styling( bootstrap_options = c("hover", "condensed"))   %>% 
  column_spec(1, width = "15%")
```


<br>

# Professional activities
```{r}
cv_entries %>% 
  filter(type == 'prof-act') %>% 
  mutate(what = str_c("<span class='cv-entry-title'>", what, "</span>, ", where)) %>% 
  select(year_begin, what) %>% 
  kbl(padding = 0, col.names = NULL, align = c("l", "l"), escape = FALSE) %>%
  kable_styling( bootstrap_options = c("hover", "condensed")) %>% 
  column_spec(1, width = "15%")  
```



<br>

# Miscelaneous
## Computing skills
```{r}
cv_entries %>% 
  filter(type == 'technical') %>% 
  mutate(icon = case_when(
    str_detect(what, "data analysis") ~ "fa-bar-chart",
    str_detect(what, "research") ~ "fa-flask",
    str_detect(what, "Web") ~ "fa-laptop"
  )) %>% 
  mutate(what = str_c("<i class='fa fa-lg ", icon, "'></i> &nbsp;<span class='cv-entry-title'>", what, "</span> ", additional_info)) %>% 
  select(type, what) %>% 
  mutate(type = "") %>% 
  kbl(padding = 0, col.names = NULL, escape=FALSE) %>%
  kable_styling( bootstrap_options = c("hover", "condensed")) 
```

<br>


## Skills & volunteering
```{r}
cv_entries %>%
  filter(type == 'volunteering') %>%
  mutate(what = str_c("<span class='cv-entry-title'>", what, "</span><br class='work-break'>", where)) %>%
  mutate(what = ifelse(!is.na(additional_info), str_c(what, "<br>", additional_info), what)) %>%
  arrange(desc(date_end)) %>% 
  select(year, what) %>%
  kbl(padding = 0, col.names = NULL, escape = FALSE)  %>%
  kable_styling( bootstrap_options = c("hover", "condensed")) %>% 
  column_spec(1, width = "15%")
```

