---
title: "Resume<br><br>"
menu: main
output:
  pdf_document:
    toc: yes
    toc_depth: '2'
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float: yes
    number_sections: no
    theme: darkly
    highlight: textmate
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
library(knitr)
library(here)
library(lubridate)
library(kableExtra)
library(DT)
library(glue)
library(readxl)
library(stringi)

# install.packages("remotes")
# remotes::install_github("mitchelloharawild/icons")
# install.packages("fontawesome")
library(fontawesome)


#### publications #####
publications <- read_csv("_content/publications.csv")

#### all other entries #####
cv_entries <- read_csv("_content/cv_entries.csv", col_types = cols(
  date = col_character(),
  date_end = col_character()
)) %>% 
  mutate(
    date = as.Date(date, format = "%Y-%m-%d"),  
    date_end = ifelse(date_end == "present", NA_character_, date_end),  # Ensure NA is character
    date_end = as.Date(date_end, format = "%Y-%m-%d")  # Convert only valid dates
  ) %>%
  mutate(
    year_begin = year(date),
    year_end = case_when(
      is.na(date_end) ~ "present",
      TRUE ~ as.character(year(date_end))
    ),
    year = if_else(year_begin == year_end, 
                   as.character(year_begin), 
                   str_c(year_begin, " --- ", year_end))
  )


blank_year_when_repeated <- function(cv_entry_tibble){
  cv_entry_tibble %>% 
    mutate(row_number = row_number()) %>% 
    mutate(year_begin = as.character(year_begin),
           year_begin = case_when(
             row_number == 1 ~ year_begin,
             year_begin == lag(year_begin) ~ str_c('<span class="repeated-year">', year_begin, '</span>'),
             year_begin != lag(year_begin) ~ year_begin
           )) %>% 
    mutate(year = if_else(!is.na(lag(year)) & lag(year) == year, 
                          str_c('<span class="repeated-year">', year, '</span>'),
                          year))
}
```

# Summary
I am a data analytics professional with experience in Healthcare IT and Revenue Cycle Management. After graduating from SUNY Geneseo in 2022 with a degree in Economics and a minor in Data Analytics, I worked at Epic Systems as a Project Manager, implementing Revenue Cycle-focused healthcare software for major organizations like Memorial Sloan Kettering Cancer Center.

At Epic, I specialized in data integration, process automation, and financial workflow optimization, working directly with hospital executives to improve operational efficiency. My experience has strengthened my skills in data analysis, software implementation, and project management within the healthcare space.

I am now looking to apply my technical and analytical expertise to solve complex challenges in healthcare technology and data-driven decision-making. 


::: {}

::::

<br>

# Work Experience
```{r}
cv_entries %>% 
  filter(type == 'work', is.na(website)) %>% 
  mutate(additional_info = replace_na(additional_info, "")) %>% 
  mutate(what = str_c("<span class='cv-entry-title'>", what, "</span><br class='work-break'>", where, "<br>", additional_info)) %>% 
  arrange(desc(date)) %>% 
  select(year, what) %>% 
  kbl(padding = 0, col.names = NULL, escape = FALSE) %>%
  kable_styling( bootstrap_options = c("hover", "condensed"))   %>% 
  column_spec(1, width = "15%")
```

<br>

# Education
```{r}
cv_entries %>% 
  filter(type == 'education') %>% 
  mutate(what = str_c( "<span class='cv-entry-title'>", 
                              what, "</span>, ", where,
                              "<br>", 
                       ifelse(is.na(additional_info), "", additional_info) 
                       , "<br>", 
                       ifelse(is.na(additional_info2), "", additional_info2))) %>% 
  select(year, what) %>% 
  kbl(padding = 0, col.names = NULL, escape = FALSE) %>%
  kable_styling( bootstrap_options = c("hover", "condensed"))   %>% 
  column_spec(1, width = "15%")

```

<br>

# Professional activities
```{r}
cv_entries %>% 
  filter(type == 'prof-act') %>% 
  mutate(what = str_c("<span class='cv-entry-title'>", what, "</span>, ", where)) %>% 
  select(year_begin, what) %>% 
  kbl(padding = 0, col.names = NULL, align = c("l", "l"), escape = FALSE) %>%
  kable_styling( bootstrap_options = c("hover", "condensed")) %>% 
  column_spec(1, width = "15%")  
```

<br>

# Miscelaneous

### Computing skills
```{r}
cv_entries %>% 
  filter(type == 'technical') %>% 
  mutate(icon = case_when(
    str_detect(what, "data analysis") ~ "fa-bar-chart",
    str_detect(what, "research") ~ "fa-flask",
    str_detect(what, "Web") ~ "fa-laptop"
  )) %>% 
  mutate(what = str_c("<i class='fa fa-lg ", icon, "'></i> &nbsp;<span class='cv-entry-title'>", what, "</span> ", additional_info)) %>% 
  select(type, what) %>% 
  mutate(type = "") %>% 
  kbl(padding = 0, col.names = NULL, escape=FALSE) %>%
  kable_styling( bootstrap_options = c("hover", "condensed")) 
```

<br>


### Skills & volunteering
```{r}
cv_entries %>%
  filter(type == 'volunteering') %>%
  mutate(what = str_c("<span class='cv-entry-title'>", what, "</span><br class='work-break'>", where)) %>%
  mutate(what = ifelse(!is.na(additional_info), str_c(what, "<br>", additional_info), what)) %>%
  arrange(desc(date_end)) %>% 
  select(year, what) %>%
  kbl(padding = 0, col.names = NULL, escape = FALSE)  %>%
  kable_styling( bootstrap_options = c("hover", "condensed")) %>% 
  column_spec(1, width = "15%")
```

